\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-07-11 tex/paper.tex
ABC and HABC notes
ABC citations

In many fields of science such as particle physics, epidemiology,  and population
genetics, computer simulators are used to describe complex data generation processes. These simulators relate 
observations $\bfx$ to the parameters $\bftheta$ of an underlying theory or mechanistic model. 
In most cases, these simulators are specified as procedural implementations of forward, stochastic processes involving latent variables $\bfz$.
% and may generate either discrete or continuous data. 
Rarely do these simulators admit a tractable density (or likelihood) $p(\bfx | \bftheta)$. The prevalence and significance of this problem has motivated an active research effort in so-called \textit{likelihood-free inference} algorithms such as Approximate Bayesian Computation (ABC)~\cite{abc, cranmer2015approximating}. 
Often the simulation code involves control-flow that implies the dependence of $\bfx$ on $\bfz$ is non-differentiable, making inference even more difficult and precludes approaches such as Ref.~\citep{2016arXiv160507826G}.

@@

@@

\bibliographystyle{acm}
\bibliography{bibliography.bib}

>>>>

In many fields of science such as particle physics, epidemiology,  and population
genetics, computer simulators are used to describe complex data generation processes. These simulators relate 
observations $\bfx$ to the parameters $\bftheta$ of an underlying theory or mechanistic model. 
In most cases, these simulators are specified as procedural implementations of forward, stochastic processes involving latent variables $\bfz$.
% and may generate either discrete or continuous data. 
Rarely do these simulators admit a tractable density (or likelihood) $p(\bfx | \bftheta)$. The prevalence and significance of this problem has motivated an active research effort in so-called \textit{likelihood-free inference} algorithms such as Approximate Bayesian Computation (ABC)~\cite{beaumont2002approximate, marjoram2003markov, sisson2007sequential, sisson2011likelihood, marin2012approximate, cranmer2015approximating}. 
Often the simulation code involves control-flow that implies the dependence of $\bfx$ on $\bfz$ is non-differentiable, making inference even more difficult and precludes approaches such as Ref.~\citep{2016arXiv160507826G}.

%\kcnote{HMC https://arxiv.org/pdf/1503.01916.pdf}

%\kcnote{add ABC refs mentioned in tex}
%(Beaumont et al., 2002; Marjoram et al., 2003; Sisson et al., 2007; Sisson \& Fan, 2010; Marin et al., 2012; Fan et al., 2013) }

@@

\citep{meeds2015hamiltonian}

@@

%\bibliographystyle{hacm}
\bibliographystyle{hunsrt}
\bibliography{bibliography.bib}
